Comparison of continuous prediction bands for the validation of biomechanical curve data

### 2021-11-12 paper.Rmd
Update paper draft

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
# library(boot)

@@

source("example_data.R")
source("pick_subwise_curves.R")
source("draw_clusters.R")
source("floa_rcb.R")
source("lenhoff_doris.R")
source("floa_point.R")
source("floa_roislien.R")
source("plot_loa.R")
source("get_coverage.R")
source("get_coverage_fraction.R")
source("get_coverage_singlecurve.R")
source("get_coverage_singlecurve_fraction.R")
source("crossval_coverage.R")
source("crossval_coverage_fraction.R")
source("singlecurve_coverage.R")
source("singlecurve_coverage_fraction.R")
source("plot_cov_ver.R")
# source("distance_2_floa.R")
source("estimate_uncertainty_loa.R")
```

>>>>

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)

@@

source("example_data.R")
source("pick_subwise_curves.R")
source("draw_clusters.R")
source("floa_rcb.R")
source("lenhoff_doris.R")
source("floa_point.R")
source("floa_roislien.R")
source("plot_loa.R")
source("get_coverage.R")
source("get_coverage_fraction.R")
source("get_coverage_singlecurve.R")
source("get_coverage_singlecurve_fraction.R")
source("crossval_coverage.R")
source("crossval_coverage_fraction.R")
source("singlecurve_coverage.R")
source("singlecurve_coverage_fraction.R")
source("plot_cov_ver.R")
source("estimate_uncertainty_loa.R")
```
